\section{Bayesian Network}
\label{sec:implementation:bayesian-network}

In \cref{sec:analysis:recommender-systems,sec:design:bayesian-network} we described our motivation to use a Bayesian network for determining the appropriate action to trigger given a context. In order to save time on the implementation of the Bayesian network, we decided investigate third party implementations.

Our requirements for the implementation were the following:

\begin{itemize}
\item The implementation should be correct, i.e. given a set of nodes with states, edges, probabilities and evidence the computed belief of the nodes should be correct.
\item The implementation should support soft evidence as described in \cref{sec:design:bayesian-network}.
\item The implementation should be written in Java.
\end{itemize}

We chose to only consider implementations written in Java as we are familiar with the language and we were confident that implementations written in Java would run on Android platforms with only little work required. 

The correctness of the implementation was validated using Hugin, a decision making tool previously described in \todo[author=Simon]{Indsæt reference til beskrivelse af Hugin.}. Given a set of nodes with states, edges, probabilities and evidence on the states, the resulting belief of the states should equal the resulting belief when the same configurations were made in Hugin.

When investigating third party solutions, we found that only few implementations supported soft evidence. Since we utilize this in the design of the Bayesian network, the implementation must support it. 

We found that the Jayes\footnote{http://www.eclipse.org/recommenders/jayes/} and Bruse\footnote{https://github.com/slangevi/bruse} implementations fulfilled our requirements. We chose to use the Jayes framework for the following reasons.

\begin{itemize}
\item The framework is maintained by Eclipse Foundation, who use it in Code Recommenders, a tool for intelligent code completion\footnote{http://www.eclipse.org/recommenders/}. The implementation being used in a large project and maintained by a foundation may be the reason it is more widespread and more information, such as documentation, is available.
\item The framework  has unit tests which eases the process of getting started using the framework as the unit tests help document how the framework is intended to be used.
\end{itemize}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../../master"
%%% End:
