\subsection{Evidence in System State Nodes}
\label{sec:design:bayesian-network:system-state-nodes-evidence}

In \Cref{fig:design:bayesian-network:overview} we suggested two nodes that supply information about the system state. The TV\_IsOn supplies information about whether not the television is on and the MusicCentre\_IsPlaying node supplies information on whether or not the music centre is playing music. Naturally these are examples of nodes that can describe the state of the system. Other examples can include if a lamp is on or not, a door is locked or unlocked or who is home.

Evidence on the system state nodes in the uppermost level is likely to be hard evidence, assuming that the state of the system retrieved from openHAB can be trusted. There could be cases where the system state returned by openHAB is not the correct state. The following are examples of cases where we may not be able to trust the state stored in openHAB.

\begin{itemize}
\item Assume a television which can be controlled though openHAB. When a request to turn on the television is send to openHAB, the request is forwarded to the television. openHAB can store the new state of the television. If some user decides to control the television using an regular TV remote, the request is not send through openHAB and unless openHAB continuously polls for the state, the state of the television is never updated in openHAB. Fortunately, openHAB supports polling of states.
\item When a request to change the state of an item is send through openHAB, the new state can be stored by openHAB if the request was successful. For some protocols, e.g. UDP, it is not known if a message is delivered correctly and therefore openHAB cannot depend on storing the state of a device only if a request is successful, except if it only use protocols that support this. Another issue with UDP is that the order of messages is unknown, hence it is unknown which state the device ends in.
\end{itemize}

When trusting the state stored in openHAB, the evidence can be hard. If the state is not trusted, one can reside to using soft evidence. E.g. based on historical data for each device.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../../master"
%%% End:
